Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-03-03 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_transiting.py}
    \begin{centering}
        \includegraphics[width=.95\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero corresponds to the transit mid-time of the planet.
        }
        \label{fig:cumdist_transiting}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_rv.py}
    \begin{centering}
        \includegraphics[width=0.95\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero is chosen arbitrarily.
        }
        \label{fig:cumdist_rv}
    \end{centering}
\end{figure*}

@@

@@

\subsubsection{GJ 1061}
GJ 1061 b is a non-transiting, likely rocky planet. We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate

>>>>

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_transiting.py}
    \begin{centering}
        \includegraphics[width=.9\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero corresponds to the transit mid-time of the planet.
        }
        \label{fig:cumdist_transiting}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{paper_cumdist_individual_rv.py}
    \begin{centering}
        \includegraphics[width=0.9\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
        \caption{
            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero is chosen arbitrarily.
        }
        \label{fig:cumdist_rv}
    \end{centering}
\end{figure*}

@@

GJ 1061 is lacking a stellar rotation period estimate, which we to calculate the magnetic field, and $v_{rel}$. \cite{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days.

@@
